%-------------------------
% Resume in Latex
% Author : Liana Severo
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[pdftex]{hyperref}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Liana Severo} & Email: \href{mailto:lianasevero3@gmail.com}{lianasevero3@gmail.com} \\
  \url{www.linkedin.com/in/liana-severo} & Mobile: 321-460-7590 \\
  \url{www.github.com/lienne} & Website: \url{https://lienne.github.io}
\end{tabular*}

%---------------SUMMARY----------------
\section{Summary}
\vspace{-3pt}
  Mid-level software engineer with expertise in full-stack development, CI/CD pipelines, and Agile methodologies. Proven track record of delivering scalable solutions and impactful user experiences using Typescript, React Native, C++, Java, and Azure DevOps. Skilled in collaborating with cross-functional teams to drive innovation and efficiency.

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
   {Microsoft}{Redmond, WA}
   {Software Engineer}{December 2020 -- September 2024}
   \begin{itemize} \itemsep -2pt  % reduce space between items
       \item Developed a taskpane for Excel's External Links feature using React Native, TypeScript and C++.
       \item Contributed to the Automatic Data Conversion Project by focusing on validation, testing, telemetry, and user data analysis, providing users control over Excel's automatic data conversions.
       \item Independently redesigned the Center Across Selection button in the Merge and Center menu for both desktop and web versions of Excel. Delivered full-stack development using C/C++, C\#, and TypeScript.
       \item Created interactive Power BI dashboards to visualize and analyze feature usage, driving data-driven decisions.
       \item Leveraged Azure DevOps for task planning, code reviews, and managing automated test pipelines. Utilized Git for version control, reviewed team members' code, and developed comprehensive test cases for my own contributions.
       \item Participated in a staged CI/CD deployment model, rolling out new features to internal testing rings before public release.
   \end{itemize}
  
  \resumeSubheading
   {JPMorgan Chase}{Tampa, FL}
   {Software Engineering Intern}{June 2020 -- August 2020}
   \begin{itemize} \itemsep -2pt  % reduce space between items
       \item Built a Networking and Training web app for a Financial Literacy nonprofit using Java Spring Boot, React, AWS, and PostgreSQL.
       \item Collaborated with a team to deliver a production-ready project as part of JPMorgan’s Code For Good initiative.
   \end{itemize}

    \resumeSubheading
      {CDK Global}{Seattle, WA}
      {Software Engineering Intern}{Summer 2018 \& Summer 2019}
    \begin{itemize} \itemsep -2pt %reduce space between items
        \item Developed web back-end tools in Java 8 and Spring Boot to automate customer lead submission processes for sales associates in dealerships around the world.
        \item Built an internal web app for data transparency, utilizing Angular and Oracle SQL.
        \item Applied Agile methodologies, DevOps processes including monitoring, logging, and code review, and used tools like Jira and Maven.
    \end{itemize}
    
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart \itemsep -2pt %reduce space between items
    \item \textbf{Languages:} Java, Python, C++, JavaScript, Typescript, SQL, \LaTeX
    \item \textbf{Frameworks/Tools:} Spring Boot, JUnit, Angular, Git, Azure DevOps, IntelliJ, Agile Methodologies
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Central Florida}{Orlando, FL}
      {Bachelor of Science in Mathematics, Minor in Computer Science}{August 2020}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Personal Projects}
    \resumeSubHeadingListStart \itemsep -2pt %reduce space between items
      \item \textbf{Modibot Project:} Open-source Discord bot using Python and the Discord.py library. \href{https://github.com/lienne/ModiBot}{GitHub Link}
      \item \textbf{Hackathon Projects:} Achieved top placements for innovative solutions. \href{https://devpost.com/lienne}{Devpost Profile}
      \item \textbf{KnightHacks Vice-President:} Organized UCF’s annual hackathon and led workshops. \href{https://www.youtube.com/watch?v=1cuhODT6MGM}{Workshop Video}
    \resumeSubHeadingListEnd
    
    
\end{document}
